\TheTitle

### 2019-03-08 Paper1/introduction.tex
vtk plot and paper continued

Here, we collect the moments for which $\vert i \vert \leq M$ holds in the moment matrix $\bm{\hat{u}}:=(\bm{\hat{u}}_0,\cdots,\bm{\hat{u}}_N)^T\in\mathbb{R}^{(N+1) \times p}$ and the corresponding basis functions in $\bm{\varphi}:=(\varphi_0,\cdots,\varphi_N)^T\in\mathbb{R}^{N+1}$. When using the stochastic-Galerkin method to close \eqref{eq:nonClosedMomentSystem}, the resulting moment system is not necessarily hyperbolic and the solution needs to be manipulated \cite{schlachter2018hyperbolicity} in order to prevent a failure of the method. A generalization of stochastic-Galerkin, which ensures hyperbolicity is the Intrusive Polynomial Moment (IPM) closure \cite{poette2009uncertainty}: The closure is given by a constraint optimization problem. For a given convex entropy $s:\mathbb{R}^p\to\mathbb{R}$ for the original problem \eqref{eq:hyperbolicProblem}, this optimization problem is given by

>>>>

Here, we collect the moments for which $\vert i \vert \leq M$ holds in the moment matrix $\bm{\hat{u}}:=(\bm{\hat{u}}_0,\cdots,\bm{\hat{u}}_N)^T\in\mathbb{R}^{(N+1) \times p}$ and the corresponding basis functions in $\bm{\varphi}:=(\varphi_0,\cdots,\varphi_N)^T\in\mathbb{R}^{N+1}$. When using the stochastic-Galerkin method to close \eqref{eq:nonClosedMomentSystem}, the resulting moment system is not necessarily hyperbolic \cite{poette2009uncertainty} and the solution needs to be manipulated \cite{schlachter2018hyperbolicity} in order to prevent a failure of the method. A generalization of stochastic-Galerkin, which ensures hyperbolicity is the Intrusive Polynomial Moment (IPM) closure \cite{poette2009uncertainty}: The closure is given by a constraint optimization problem. For a given convex entropy $s:\mathbb{R}^p\to\mathbb{R}$ for the original problem \eqref{eq:hyperbolicProblem}, this optimization problem is given by
